Fitting phylogenetic generalized linear mixed models

### 2017-11-07 ms.tex
master equation

\usepackage{alltt}
\usepackage[sort]{natbib}
\usepackage{amsmath}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage[utf8]{inputenc} % for accented characters
%% stuff for editing
%\usepackage[markup=nocolor,addedmarkup=bf,deletedmarkup=sout]{changes}
%% to suppress notes & comments: \usepackage[final]{changes}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{setspace}
\bibliographystyle{chicago}
\title{Fitting phylogenetic generalized linear mixed-effect models using lme4 }
\author{Michael Li and Ben Bolker}
\date{\today}

@@

We simulated two phenotypic traits. Trait $Y$ of species $i$ ($i$ = 1,...,$n$) that depends on a trait X using the model:

\ml{Y~X + (1+X|phylo) and the 3 forms in ols/gls} 
\begin{align}
Y & = \alpha_{0} + \alpha_{1}X + \beta (1+X) + \epsilon 
\\
\beta & \sim \mathrm{MVN}(0,\Sigma)
\\
\epsilon & \sim \mathrm{N}(0, \sigma^2_{n})
\end{align}

where

\begin{align}
\Sigma & = \begin{pmatrix} \sigma^2_{sp} & \rho \sigma_{sp} \sigma_{X} \\ \rho \sigma_{sp} \sigma_{X} & \sigma^2_{X} \end{pmatrix}
\end{align}
We assumed both phenotypic trait are measured. X (e.g. ...) affects

\ml{metabolism example?}

\ml{ditto above with multiple sites}
\subsection{Phylogenetic Tree Transformation}
The standard problem of phylogenetic comparative methods is to analyze relationships among data where the observations are gathered from nodes (usually tips) of a phylogenetic tree.

>>>>

\usepackage{alltt}
\usepackage[sort]{natbib}
\usepackage{amsmath}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage[utf8]{inputenc} % for accented characters
%% stuff for editing
%\usepackage[markup=nocolor,addedmarkup=bf,deletedmarkup=sout]{changes}
%% to suppress notes & comments: \usepackage[final]{changes}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{setspace}
\bibliographystyle{chicago}
\title{Fitting phylogenetic generalized linear mixed models}
\author{Michael Li and Ben Bolker}
\date{\today}

@@

%We simulated two phenotypic traits (X andY). 
The typical phylogenetic linear mixed model analysis is of the form:

\begin{align}
(Y \mid B=b) & \sim N(X\beta + Zb, \sigma^{2}),
\end{align}
where the conditional distribution of Y given $ B = b$ is a $n \times 1$ vector random response variable, whose observed value is y of some measureable phenotypic trait; 
X is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independent variables (traits);
Z is an $n \times (m + 1)$ model matrix for the $m + 1$ -- dimensional vector-valued random effects variable; 
$\beta$ is a $ m + 1 $ coefficient vector.
The parameters of the model are the coefficients $\beta$ and the scale parameter $\sigma$.
The unconditional distribution of B is multivariate normal with mean zero and a parameterized $(m + 1) \times (m + 1)$ variance-covariance matrix
\begin{align}
B & \sim \mathrm{MVN}(0,\Sigma),
\end{align}
and
\begin{align}
\Sigma & = \begin{pmatrix} \sigma^2_{sp} & \rho \sigma_{sp} \sigma_{X} \\ \rho \sigma_{sp} \sigma_{X} & \sigma^2_{X} \end{pmatrix},
\end{align}
where $\sigma^{2}_{sp}$ and $\sigma^{2}_{X}$ is the phylogenetic variance of species and phenotype X; 
and $\rho$ is the correlation of \ml{...?}.

\subsection{Phylogenetic Tree Transformation}
The standard problem of phylogenetic comparative methods is to analyze relationships among data where the observations are gathered from nodes (usually tips) of a phylogenetic tree.
